Differentially Private Bayesian Inference

### 2018-04-26 main.tex
fixed the biblio
working on the style

\subsubsection{Algorithm Setting up}
The candidate set and utility function are still the same as before, differ only in the sensitivity. It will output a candidate $r \in R$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 S(x)})$:

\begin{equation*}
P[r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 S(x)})}
{\Sigma_{r' \in R}\ exp(\frac{\epsilon u(x,r')}{2 S(x)})},
\end{equation*}
where the sensitivity in mechanism is smooth sensitivity $S(x)$\cite{nissim2007smooth}, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}u(x), \max_{y \neq x; y \in D^{n}}(\Delta_{l}u(y)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $\beta = \beta(\epsilon, \delta)$. In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.

\subsubsection{Sliding Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the sliding property holds:

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

\begin{proof}
We firstly proof that $Pr[\expomech = z] = \underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)]$. Then we can use the exponential probability in following proofs. From the output probability of every candidate $r$ in $\expomech$, $Pr[\expomech = z] \sim u(z,x)$. We can derive, if $u(z,x) = u(z',x)$ then $Pr[\expomech = z] = Pr[\expomech = z']$. We assume the number of candidates $r \in \mathsf{R}$ that satisfy $u(z,x) = u(r,x)$ is $|z|$, we have  $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = |z| Pr[\expomech = z]$. In our case, $u(r,x)$ come from Hellinger distance is axial symmetry, where the true output is the symmetry axis. It can be infer that |z| = 2 for any candidates, apart from the true output, i.e., $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = 2 Pr[\expomech = z]$. This parameter can be eliminate in both sides in proving.

@@

\printbibliography

>>>>

\subsubsection{Algorithm Setting up}
We define a new mechanism $\hexpmech(x)$
which is similar to the exponential mechanism where we use
$\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters
summing up to $n+2$, as scoring function we use the Hellinger distance
from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we 
calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The
only difference is in the sensitivity part, since now we use the
smooth sensitivity.

\begin{definition} The mechanism $\hexpmech(x)$ outputs a candidate $r \in \betaset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[z=r] = \frac
{exp(\frac{-\epsilon\hlg(\bysinfer(x),r)}{2 S_\beta(x)})}
{\Sigma_{r' \in R}\ exp(\frac{-\epsilon \hlg(\bysinfer(x),r')}{2 S_\beta(x)})},
\end{equation*}
where $s_\beta(x)$ is the smooth sensitivity of $\hlg(\bysinfer(x),-)$, calculated by:
\begin{equation*}
S_{\beta}(x) = \max(\Delta_{l}\hlg(\bysinfer(x),-), \max_{y \neq x; y \in D^{n}}(\Delta_{l}\hlg(\bysinfer(x),-)\cdot e^{-\beta d(x,y)})),
\end{equation*}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\betaset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\betaset$ we have:
$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]\Big )
$$
To see this, it is enough to notice that ...

 From the output probability of every candidate $r$ in $\expomech$, $Pr[\expomech = z] \sim u(z,x)$. We can derive, if $u(z,x) = u(z',x)$ then $Pr[\expomech = z] = Pr[\expomech = z']$. We assume the number of candidates $r \in \mathsf{R}$ that satisfy $u(z,x) = u(r,x)$ is $|z|$, we have  $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = |z| Pr[\expomech = z]$. In our case, $u(r,x)$ come from Hellinger distance is axial symmetry, where the true output is the symmetry axis. It can be infer that |z| = 2 for any candidates, apart from the true output, i.e., $\underset{r \thicksim \expomech}{Pr}[u(r,x) = u(z,x)] = 2 Pr[\expomech = z]$. This parameter can be eliminate in both sides in proving.

In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.

\subsubsection{Sliding Property of Exponential Mechanism}
\begin{lem}
Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \expomech}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

@@

\bibliographystyle{plain}
\bibliography{bayesian.bib}
